Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value

### 2021-08-27 docs/revision/manuscript-revised.Rmd
update: add Meta-Psych open peer review statement

---
title             : "Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value"
shorttitle        : "Meta-analysis of self-controlled research"
author: 
  - name          : "Brad McKay"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "1280 Main Street West, Ivor Wynne Centre Room AB-131 A1, McMaster University, Hamilton ON Canada, L8S 4K1"
    email         : "bradmckay8@gmail.com"
  - name          : "Zachary D. Yantha"
    affiliation   : "1"
  - name          : "Julia Hussien"
    affiliation   : "1"
  - name          : "Michael J. Carter"
    affiliation   : "2"
  - name          : "Diane M. Ste-Marie"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "School of Human Kinetics, University of Ottawa"
  - id            : "2"
    institution   : "Department of Kinesiology, McMaster University"

authornote: |
  \vspace{-3em}
  \addORCIDlink{Brad McKay}{0000-0002-7408-2323} \newline
  \indent\addORCIDlink{Julia Hussien}{0000-0001-7434-228X}  
  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}  
  \addORCIDlink{Zachary D. Yantha}{0000-0003-1851-7609}  
  \addORCIDlink{Diane M. Ste-Marie}{0000-0002-4574-9539}

>>>>

---
title             : "Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value"
shorttitle        : "Meta-analysis of self-controlled research"
author: 
  - name          : "Brad McKay"
    affiliation   : "1,2"
    corresponding : no    # Define only one corresponding author
    address       : "1280 Main St W, IWC AB-131 A1, McMaster University, Hamilton ON Canada, L8S 4K1"
    email         : "bradmckay8@gmail.com"
  - name          : "Zachary D. Yantha"
    affiliation   : "1"
  - name          : "Julia Hussien"
    affiliation   : "1"
  - name          : "Michael J. Carter"
    affiliation   : "2"
  - name          : "Diane M. Ste-Marie"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "School of Human Kinetics University of Ottawa"
  - id            : "2"
    institution   : "Department of Kinesiology McMaster University"

authornote: |
  Submitted to *Meta-Psychology*. Participate in open peer review by commenting through hypothes.is directly on this preprint. The full editorial process of articles under review at *Meta-Psychology* can be found here: https://tinyurl.com/mp-submissions. You will find this preprint by searching for the first authors name.

  \newpage
  \addORCIDlink{Brad McKay}{0000-0002-7408-2323} \newline
  \indent\addORCIDlink{Julia Hussien}{0000-0001-7434-228X}  
  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}  
  \addORCIDlink{Zachary D. Yantha}{0000-0003-1851-7609}  
  \addORCIDlink{Diane M. Ste-Marie}{0000-0002-4574-9539}

### 2021-08-27 docs/revision/manuscript-revised.tex
update: add Meta-Psych open peer review statement

\vspace{-3em}

@@

Correspondence concerning this article should be addressed to Brad McKay, 1280 Main Street West, Ivor Wynne Centre Room AB-131 A1, McMaster University, Hamilton ON Canada, L8S 4K1. E-mail: \href{mailto:bradmckay8@gmail.com}{\nolinkurl{bradmckay8@gmail.com}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Human Kinetics, University of Ottawa\\\textsuperscript{2} Department of Kinesiology, McMaster University}

>>>>

Submitted to \emph{Meta-Psychology}. Participate in open peer review by commenting through hypothes.is directly on this preprint. The full editorial process of articles under review at \emph{Meta-Psychology} can be found here: \url{https://tinyurl.com/mp-submissions}. You will find this preprint by searching for the first authors name.

\newpage

@@

Correspondence concerning this article should be addressed to Brad McKay, 1280 Main St W, IWC AB-131 A1, McMaster University, Hamilton ON Canada, L8S 4K1. E-mail: \href{mailto:bradmckay8@gmail.com}{\nolinkurl{bradmckay8@gmail.com}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Human Kinetics University of Ottawa\\\textsuperscript{2} Department of Kinesiology McMaster University}
